Datasheet for 'New York Bridge 2016

### 2024-12-04 other/datasheet/datasheet.qmd
Final prose update

The "New York Bridges 2016" dataset was created to document and assess the structural conditions and administrative details of bridges across New York State, supporting infrastructure management, maintenance prioritization, and policy-making. Developed by the New York State Department of Transportation (NYSDOT) and made publicly available through the Data and Story Library (DASL), this dataset addresses the need for standardized, comprehensive data on bridge deterioration influenced by geographic, administrative, and traffic-related factors. Funded as part of New York State’s infrastructure monitoring programs, the dataset serves as a vital resource for researchers, policymakers, and engineers, enabling data-driven decision-making to enhance public safety and infrastructure sustainability.

@@

The dataset is comprehensive rather than a sample, aiming to capture all operational bridges in New York State as of 2016. This ensures extensive geographic and administrative coverage, from urban centers with high traffic density to rural bridges with lower traffic loads. While the data is representative, rural bridges may have less frequent or less detailed inspections, potentially introducing a minor bias.

@@

The dataset titled "New_York_Bridges_2016" was originally compiled by the New York State Open Data platform[@ny_open_data_2020], with county-level contributions from the New York State Department of Transportation [@county_data]. Accessed via the Data And Story Library [@dasl_data_2016], which archives historical datasets for academic and public use, it represents a comprehensive resource for understanding bridge conditions across New York State.

@@

The primary mechanisms for data collection included on-site manual inspections supported by tools like measurement instruments and inspection checklists. Administrative details, such as ownership, were sourced from official state databases. NYSDOT ensured the reliability of these processes through rigorous training programs for inspectors and periodic calibration of measurement tools. The dataset is comprehensive, capturing all operational bridges in the state as of 2016, rather than representing a sample, and thus no specific sampling strategy was required.

@@

In summary, the New York Bridges 2016 dataset was compiled through standardized field inspections and administrative records, validated by trained professionals, and ethically sound due to its exclusive focus on public infrastructure. Its methodology ensures high-quality, accurate data for research, policy planning, and infrastructure management, while DASL plays a critical role in archiving and maintaining this resource for public and academic use.

@@

The New York State Bridge Conditions dataset, also utilized in the ARTBA's bridge report[@ARTBA], has been applied to analyze the structural conditions of bridges across New York. The dataset helps identify structurally deficient bridges, prioritize infrastructure projects, and allocate federal funds, such as the $2 billion bridge formula funds under the Infrastructure Investment and Jobs Act (IIJA). This dataset is well-suited for tasks like policy development, maintenance scheduling, risk assessment, and infrastructure planning, offering actionable insights into bridge management. However, its composition reflects current bridge conditions and may not fully account for recently completed repairs, which could influence its applicability for real-time analyses. The dataset is tailored to infrastructure evaluations and is not recommended for unrelated uses. Overall, it serves as a critical resource for understanding and improving bridge conditions in New York State.

>>>>

The "New York Bridges 2016" dataset was created to document and assess the structural conditions and administrative details of bridges across New York State, supporting infrastructure management, maintenance prioritization, and policy-making. Developed by the New York State Department of Transportation (NYSDOT) and made publicly available through the Data and Story Library (DASL), this dataset addresses the need for data on bridge deterioration influenced by geographic, administrative, and traffic-related factors. Funded as part of New York State’s infrastructure monitoring programs, the dataset serves as a vital resource for researchers, policymakers, and engineers, enabling informed decision-making to enhance public safety and infrastructure sustainability.

@@

The dataset aims to include all operational bridges in New York State as of 2016, providing broad geographic and administrative coverage, from urban centers with high traffic density to rural bridges with lower traffic loads. While the data is representative, rural bridges may have less frequent or less detailed inspections, potentially introducing a minor bias.

@@

The dataset titled "New_York_Bridges_2016" was originally compiled by the New York State Open Data platform[@ny_open_data_2020], with county-level contributions from the New York State Department of Transportation [@county_data]. Accessed via the Data And Story Library [@dasl_data_2016], which archives historical datasets for academic and public use, it represents a resource for understanding bridge conditions across New York State.

@@

The primary mechanisms for data collection included on-site manual inspections supported by tools like measurement instruments and inspection checklists. Administrative details, such as ownership, were sourced from official state databases. NYSDOT ensured the reliability of these processes through rigorous training programs for inspectors and periodic calibration of measurement tools. The dataset capturing all operational bridges in the state as of 2016, rather than representing a sample, and thus no specific sampling strategy was required.

@@

In summary, the New York Bridges 2016 dataset was compiled through standardized field inspections and administrative records, validated by trained professionals, and ethically sound due to its exclusive focus on public infrastructure. Its methodology ensures high-quality, accurate data for research, policy planning, and infrastructure management, while DASL plays a role in archiving and maintaining this resource for public and academic use.

@@

The New York State Bridge Conditions dataset, also utilized in the ARTBA's bridge report[@ARTBA], has been applied to analyze the structural conditions of bridges across New York. The dataset helps identify structurally deficient bridges, prioritize infrastructure projects, and allocate federal funds, such as the $2 billion bridge formula funds under the Infrastructure Investment and Jobs Act (IIJA). This dataset is well-suited for tasks like policy development, maintenance scheduling, risk assessment, and infrastructure planning, offering actionable information into bridge management. However, its composition reflects current bridge conditions and may not fully account for recently completed repairs, which could influence its applicability for real-time analyses. The dataset is tailored to infrastructure evaluations and is not recommended for unrelated uses. Overall, it serves as a resource for understanding and improving bridge conditions in New York State.
